### 2020-02-14 thesis/paper.tex
prep

\subsubsection{DBSCAN}
Another data-set for which this method works is Zahn's Compound \cite{1671676} which combines multiple difficult clustering tasks. The combined data-set can be seen in \ref{fig:zahn} with its intended labels.

@@

>>>>

\subsubsection{DBSCAN}
Another data-set for which this method works is Zahn's Compound \cite{1671676} which combines multiple difficult clustering tasks. The combined data-set can be seen in \ref{fig:zahn} with its intended labels. If was standardized first, to be able to easier define DBSCAN parameters.

@@

\section{Unobtainable Solutions}
Single clustering algorithms may not be able to find the structure of a data-set when different kinds of structures are present for different clusters. Combining results of different clustering algorithms may solve this problem, as correctly identified structures should be robust throughout multiple runs of a fitting algorithm while they should not be robust whenever the algorithm doesn't fit the structure. To illustrate this a data-set was created combining a density based cluster with Gaussian clusters with different deviations, see Figure ....

NMI best: 0.872
NMI Cons: 0.978
